---
title: "Take-home Exercise 5"
description: 
  
author:
  - name: Chu Yi Ning 
    url: 
    affiliation: SMU MITB
    affiliation_url: 
date: "`r Sys.Date()`"
output: distill::distill_article
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Getting Started 

We will use the following packages for this exercise.

```{r}
packages = c('sf', 'tmap', 'tidyverse', 
             'lubridate', 'clock', 
             'sftime', 'rmarkdown')
for (p in packages){
  if(!require(p, character.only = T)){
    install.packages(p)
  }
  library(p,character.only = T)
}
```

# Data

As we are processing spatial data, *read_sf* will be used to load data.

```{r}
schools <- read_sf("data/Schools.csv", 
                   options = "GEOM_POSSIBLE_NAMES=location")  
pubs <- read_sf("data/Pubs.csv", 
                   options = "GEOM_POSSIBLE_NAMES=location")
apartments <- read_sf("data/Apartments.csv", 
                   options = "GEOM_POSSIBLE_NAMES=location")
buildings <- read_sf("data/Buildings.csv", 
                   options = "GEOM_POSSIBLE_NAMES=location")
employers <- read_sf("data/Employers.csv", 
                   options = "GEOM_POSSIBLE_NAMES=location")
restaurants <- read_sf("data/Restaurants.csv", 
                   options = "GEOM_POSSIBLE_NAMES=location")
```


From the plot below, we can see that the most obvious dots are light blue and red dots which represent apartments and work places, respectively. When comparing apartments and work place, the former is located closer to the centre.

```{r}
tmap_mode("plot")
tm_shape(buildings)+
tm_polygons(col = "grey70",
            size = 1,
            border.col = "black",
            border.lwd = 1) +
tm_shape(employers) +
  tm_dots(size = 0.05, col = "red") +
tm_shape(apartments) +
  tm_dots(size = 0.05, col = "lightblue") +
tm_shape(pubs) +
  tm_dots(size = 0.05, col = "purple") +
tm_shape(restaurants) +
  tm_dots(size = 0.05, col = "darkblue") +
tm_shape(schools) +
  tm_dots(size = 0.05, col = "orange")
tmap_mode("plot")
```


Data for our study are for the period of 1st March 2022 to 6th March 2022.

```{r}
logs <- read_sf("data/ParticipantStatusLogs1.csv", 
                options = "GEOM_POSSIBLE_NAMES=currentLocation")
```


As we only focus on traffic, we will filter *Transport* from currentMode.

```{r}
logs_selected <- logs %>%
  filter(currentMode == "Transport")
```




```{r}
hex <- st_make_grid(buildings, 
                    cellsize=100, 
                    square=FALSE) %>%
  st_sf() %>%
  rowid_to_column('hex_id')
plot(hex)
```

```{r}
points_in_hex <- st_join(logs_selected, 
                         hex, 
                         join=st_within)
```

```{r, echo = FALSE, results = FALSE}
points_in_hex <- st_join(logs_selected, 
                        hex, 
                        join=st_within) %>%
  st_set_geometry(NULL) %>%
  count(name='pointCount', hex_id)
head(points_in_hex)
```

```{r}
hex_combined <- hex %>%
  left_join(points_in_hex, 
            by = 'hex_id') %>%
  replace(is.na(.), 0)
```


The darker area indicates the heavier traffic.

```{r}
tm_shape(hex_combined %>%
           filter(pointCount > 0))+
  tm_fill("pointCount",
          n = 10,
          style = "quantile") +
  tm_borders(alpha = 0.1)
```





